\documentclass[11pt,a4paper]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ankan Das} \\ \vspace{2pt}
    \small Kolkata, India $|$ +91 7890514406 $|$ \href{mailto:dasankan210@gmail.com}{\underline{dasankan210@gmail.com}} \\ \vspace{1pt}
    \href{https://github.com/mossheadzoro}{\underline{GitHub}} $|$ 
    \href{https://linkedin.com/in/ankan-das-240082328/}{\underline{LinkedIn}} $|$ 
    \href{https://ankan-portfolio-delta.vercel.app/}{\underline{Portfolio}} $|$ 
    \href{https://3-d-portfolio-seven-delta.vercel.app/}{\underline{3D Portfolio}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Techno India University}{Kolkata, India}
      {B.Tech in Computer Science \& Engineering}{2023 -- Present}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Moual (Stealth Startup)}{2026 -- Present}
      {Founder \& Lead Engineer}{}
      \resumeItemListStart
        \resumeItem{Architecting India's first AI-powered cloud ERP platform tailored for the modern jewelry retail industry.}
        \resumeItem{Engineering a high-performance, multi-tenant system to handle complex inventory workflows, automated billing, and multi-branch synchronization.}
        \resumeItem{Designing and prototyping an IoT-enabled RFID tracking system module to automate physical stock audits.}
        \resumeItem{Developing the scalable backend architecture using Node.js and PostgreSQL to ensure data integrity across parallel transactions.}
      \resumeItemListEnd

    \resumeSubheading
      {Neurathon 2026}{Feb 2026}
      {Frontend and Integration Developer (Finalist)}{}
      \resumeItemListStart
        \resumeItem{Built and deployed a working MVP of 'Event-Swarm', a multi-agent AI orchestration platform, during a 48-hour continuous hackathon.}
        \resumeItem{Designed a platform bridging the gap between simple chatbot interfaces and complex enterprise automation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Civic Fix (Smart India Hackathon Project)} $|$ \emph{React Native, Node.js, MongoDB, AI Orchestration}}{}
          \resumeItemListStart
            \resumeItem{Developed an MVP for the Smart India Hackathon (SIH), securing a spot as a campus finalist for solving real-world municipal challenges.}
            \resumeItem{Built a location-aware mobile app featuring Role-Based Access Control (RBAC) with unique dashboards for Citizens, Workers, and Municipal Heads.}
            \resumeItem{Implemented dynamic geo-fencing that auto-updates local civic issues in real-time when a user changes their city location.}
            \resumeItem{Engineered an AI dispatch engine that parses complaint details to automatically route tasks to available field workers and track resource usage.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{3D-Portfolio} $|$ \emph{Three.js, React Three Fiber, Blender, Framer Motion}}{}
          \resumeItemListStart
            \resumeItem{Built an immersive, gamified "One Piece" 3D world using React Three Fiber and Three.js.}
            \resumeItem{Modeled custom low-poly assets in Blender with baked textures, utilizing GLTF compression for optimal web performance.}
            \resumeItem{Implemented complex scroll animations, raycast interactions, and physics via Framer Motion.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hire Junc (Smart India Hackathon Project)} $|$ \emph{Node.js, Express, React, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{Built a freelance application supporting a real-time escrow system to ensure secure transactions.}
            \resumeItem{Integrated an algorithm-based work-suggestion engine to assist new freelancers in finding relevant opportunities.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Eco-Home (UN SDG 7 Alignment Project)} $|$ \emph{Python, React, MongoDB, AI Integration}}{}
          \resumeItemListStart
            \resumeItem{Developed an AI-based energy-saving system for homes and apartments.}
            \resumeItem{Created features to track electricity bills and appliances, actively recommending opportunities to reduce carbon footprints and save money.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, Python, HTML/CSS} \\
     \textbf{Frontend}{: React, Next.js, Redux, Tailwind CSS, Three.js, Vite.js, Framer Motion} \\
     \textbf{Backend \& Databases}{: Node.js, Express, PostgreSQL, MongoDB, GraphQL, Redis} \\
     \textbf{DevOps \& Cloud}{: Docker, Kubernetes, AWS, Jenkins, Git, NGINX} \\
     \textbf{Design \& 3D}{: Figma, Blender, Prototyping, Wireframing}
    }}
 \end{itemize}

\end{document}
